Software Defect Prediction: Review, Commentary, and Future Work

### 2015-12-15 paper/paper.tex
Added statistical tests and context aware cross-prroject ranking

@@

\subsection{Context Factors}
Context factors for projects were assessed by Fend at el (2014 cite here). Used as a measurement of project similarity. The provides a set of measurements to rank a project's relatedness when performing cross-project defect prediction.

@@

\subsection{Ranking}

>>>>

\section{Statistical Tests}
\subsection{Mann-Whitney U test}
The Mann-Whitney U test, a non-parametric test that determines if two independent distributions have equally large value,  was used by Zhang et al \cite{Zhang:2014:TBU:2597073.2597078} to pair-wise compare the distribution of metrics of projects in the domain of cross-project defect prediction.

@@

\subsection{Context Factors}
Context factors for projects were assessed by Zhanget et al \cite{Zhang:2014:TBU:2597073.2597078}  Used as a measurement of project similarity. The provides a set of measurements to rank a project's relatedness when performing cross-project defect prediction.

@@

\subsection{Context-Aware Rank Tranformation}
Zhang et al \cite{Zhang:2014:TBU:2597073.2597078} propose a context-aware rank transformation approach. First, split the project up into non-overlapped groups based on the previous context factors. Then cluster the groups with similar context factor distributions. Obtain a ranking function based using the 10th quantiles of predictors. Apply this ranking function to bin the predictor values into the 10 levels.
